Minimizing post-shock forecasting error through aggregation of outside information

### 2021-01-11 Revision/manuscript.tex
made minor changes to manuscript; added to the organization of Section 4

In this section we provide justification for our methods based on Monte Carlo simulation. We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.  We consider $p=25$ and $\mu_{\alpha}=2$, where $p = 25$ is set to satisfy conditions in Proposition \ref{uniqueness}. The parameter setup of our simulations is detailed as follows: 
\begin{align*}
  \phi_i &\simiid U(0,1),	\\
  \delta_i &\simiid  \normal{1}{0.5}, \\
  \theta_i &\simiid \normal{0}{1}, \\
  \alpha_i &\simiid \normal{\mu_\alpha}{\sigma_{\alpha}^2}, \\
  T_i &\simiid \min\left(90, [\text{Gamma}(15,10)]\right), \\
  T_i^* &\simiid U(p+4, T_i-1), \\
  \varepsilon_{i,t} &\simiid \normal{0}{\sigma^2}
\end{align*}
where the $[\cdot]$ operation in the generation of the $T_i$s corresponds to rounding the input to the nearest integer and the discrete uniform distribution is used to generate the $T_i^*$s. The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. Moreover, it is  designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. Additionally, we generated all of the entries of the covariate vectors to be realizations from a $\text{Gamma}(1,2)$ distribution.

@@

We discuss simulation results for the bootstrap procedures used in estimating parameters for risk-reduction propositions and inequalities. We mainly discuss simulations under $\mc{M}_2$ (see Section \ref{modelsetup}) for $\mc{B}_u$ and $\mc{B}_f$ (see Section \ref{varbootstrap}) with comparisons to those under $\mc{M}_1$ whose results are listed in Section 3 in the Supplementary Materials. Two simulation setups are investigated.

In the first simulation setup, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma=10$. Note that $\E{\E{\alpha_1}}=52$, where the last expectation is operated under the density of the covariates. In other words, data with $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$  should well represent the situations when the signal of the covariates is strong and when it is nearly lost. Results are displayed in Table~\ref{table1} in the Appendix, Section \ref{tablesappendix}.

@@

Simulation for $\mc{B}_f$ with the same parameter setup as that of $\mc{B}_u$ are implemented. See Table \ref{table3} and Table \ref{table4} for results in the Appendix, Section \ref{tablesappendix}. From Table \ref{table1} and Table \ref{table3} we have that when $n$ is moderately small ($n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is preferable to $\mc{B}_f$. For other situations, $\mc{B}_u$  and $\mc{B}_f$ perform similarly. It is likely that the extra randomness from sampling the donor pool with replacement compensates for the possible noises from a small donor pool. Concerning  Table \ref{table2} and Table \ref{table4}, it appears that when $n = 10$ and $\sigma_{\alpha}=5$, $\mc{B}_u$ is better than  $\mc{B}_f$  when $\sigma$ increases. It might be the case that additional layer of bootstrap in the donor pool buffers the negative effects on $\bar{\mc{C}}(\delta_{\hat{\alpha}})$  introduced from increasing variation of $y_{i,t}$. However, when $\sigma_{\alpha}$ increases over 5 and $n = 10$,  $\mc{B}_f$ and $\mc{B}_u$ are quite similar under  situations of different $\sigma$ and $\sigma_{\alpha}$. In conclusion, $\mc{B}_u$ is better than $\mc{B}_f$ when the signal of the covariates is strong and $n$ is moderately small; otherwise, they are similar.

>>>>

In this section we provide justification for our methods based on Monte Carlo simulation. We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.  We consider $p=25$ and $\mu_{\alpha}=2$, where $p = 25$ is set to satisfy conditions in Proposition \ref{uniqueness}. The parameter setup of our simulations is detailed as follows: 
\begin{align*}
  \phi_i &\simiid U(0,1),	\\
  \delta_i &\simiid  \normal{1}{0.5^2}, \\
  \theta_i &\simiid \normal{0}{1}, \\
  \alpha_i &\simiid \normal{\mu_\alpha}{\sigma_{\alpha}^2}, \\
  T_i &\simiid \min\left(90, [\text{Gamma}(15,10)]\right), \\
  T_i^* &\simiid U(p+4, T_i-1), \\
  \varepsilon_{i,t} &\simiid \normal{0}{\sigma^2},
\end{align*}
where the $[\cdot]$ operation in the generation of the $T_i$s corresponds to rounding the input to the nearest integer and the discrete uniform distribution is used to generate the $T_i^*$s. The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. Moreover, it is  designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. Additionally, we generated all of the entries of the covariate vectors to be realizations from a $\text{Gamma}(1,2)$ distribution.

@@

We discuss simulation results for the bootstrap procedures used in estimating parameters for risk-reduction propositions and inequalities. We mainly discuss simulations under model $\mc{M}_2$ and both bootstrap procedures, $\mc{B}_u$ and $\mc{B}_f$. Complementary simulations under $\mc{M}_1$ are provided in Section 3 of the Supplementary Materials. We now present the two simulation setups that are investigated in the main text.

In the first simulation setup we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma=10$. Note that $\E{\E{\alpha_1}}=52$, where the last expectation is operated under the density of the covariates. In other words, data with $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$  should well represent the situations when the signal of the covariates is strong and when it is nearly lost. Results are displayed in Table~\ref{table1} in the Appendix, Section \ref{tablesappendix}.

@@

\subsection{Additional considerations}
\label{parametricbootstrapsimulation2}

We now present results from simulations under bootstrap procedure $\mc{B}_f$ under the same two parameter setups considered above. See Table \ref{table3} and Table \ref{table4} for results in the Appendix, Section \ref{tablesappendix}. From Table \ref{table1} and Table \ref{table3} we have that when $n$ is moderately small ($n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is preferable to $\mc{B}_f$. For other situations, $\mc{B}_u$  and $\mc{B}_f$ perform similarly. It is likely that the extra randomness from sampling the donor pool with replacement compensates for the possible noises from a small donor pool. Concerning  Table \ref{table2} and Table \ref{table4}, it appears that when $n = 10$ and $\sigma_{\alpha}=5$, $\mc{B}_u$ is better than  $\mc{B}_f$  when $\sigma$ increases. It might be the case that additional layer of bootstrap in the donor pool buffers the negative effects on $\bar{\mc{C}}(\delta_{\hat{\alpha}})$  introduced from increasing variation of $y_{i,t}$. However, when $\sigma_{\alpha}$ increases over 5 and $n = 10$,  $\mc{B}_f$ and $\mc{B}_u$ are quite similar under  situations of different $\sigma$ and $\sigma_{\alpha}$. In conclusion, $\mc{B}_u$ is better than $\mc{B}_f$ when the signal of the covariates is strong and $n$ is moderately small; otherwise, they are similar.
